\textls[-0]{\thetitle}

### 2023-03-18 metatheory2.tex
question about linkage transformers

\subsection{MLTT with Explicit Substitutions and Universe Levels}

@@

% Copy and Paste Intuition of MLTT from other places to here
\subsection{Declarative Syntax for \TT : an MLTT variant with Linkages}
Compared to MLTT, \TT has 3 more judgements about signatures and linkage transformers. Moreover, the linkage transformer can be considered as a syntactic sugar (or ``library functions'' in the main text) (we will show why at the end). 
Since it is a syntactic sugar, we will not consider about the linkage transformers during meta-theoretic reasoning.

@@

@@

\subsection{Linkage Transformer as Syntax Sugar}
Observe the syntax, linkage transformer and its judgement is defined above 
other parts.

So we can inductively define the syntax sugar $\goodInh{\Gm}{h}{\lsig_1}{\lsig_2}$ using constructors $\InhExt{}{}$, $\InhOv{}{}$, $\InhInh{}$, $\InhNest{}{}$. Then we define the $\inh{h}{\ell}$ and the explicit substitution for linkage transformer $\sub{h}{\gm}$ by induction on the structure of linkage transformer $h$, based on the equality
%\EDJ{Add substitution equalities for linkage transformers} 
given in the syntax. In that way, the explicit substituon for linkage transformer becomes meta-level substitution again; and $\inh{h}{\ell}$ is not itself a syntax but a meta-level computation that leads to a syntax.

>>>>

\subsection{MLTT with Explicit Substitutions and Universe Levels}
\label{sec:mltt-full}

@@

% Copy and Paste Intuition of MLTT from other places to here
\subsection{\TT}
\label{sec:fmltt-full}

\TT extends the MLTT in \cref{sec:mltt-full} with W-type signatures and W-types,
linkage signatures and linkages, and linkage transformers.

@@

\noindentparagraph{Linkage transformers as syntactic sugar.}

%Moreover, the linkage transformer can be considered as a syntactic sugar (or
%``library functions'' in the main text) (we will show why at the end).
%Since it is a syntactic sugar, we will not consider about the linkage
%transformers during meta-theoretic reasoning.

%Observe the syntax, linkage transformer and its judgement is defined above 
%other parts. 
%
%So we can inductively define the syntax sugar $\goodInh{\Gm}{h}{\lsig_1}{\lsig_2}$ using constructors $\InhExt{}{}$, $\InhOv{}{}$, $\InhInh{}$, $\InhNest{}{}$. Then we define the $\inh{h}{\ell}$ and the explicit substitution for linkage transformer $\sub{h}{\gm}$ by induction on the structure of linkage transformer $h$, based on the equality
%%\EDJ{Add substitution equalities for linkage transformers} 
%given in the syntax. In that way, the explicit substituon for linkage transformer becomes meta-level substitution again; and $\inh{h}{\ell}$ is not itself a syntax but a meta-level computation that leads to a syntax.

As mentioned in \cref{sec:metatheory2}, the five forms of linkage transformers can be
thought of a library of functions that are used to construct linkages from other
linkages.
In particular, their typing rules are defined in terms of the rest of the typing
rules in \TT.
Thus, linkage transformers $\goodInh{\Gm}{h}{\lsig_1}{\lsig_2}$ can be defined
as syntactic sugar via an inductive type with constructors\YZ{I reinterpreted what you wrote, but this sentence doesn't sound right to me. If linkage transformers are meta-level inductive types, aren't they just part of the syntax?}
$\InhExt{}{}$, $\InhOv{}{}$, $\InhInh{}$, $\InhNest{}{}$, and
the syntax $\inh{h}{\ell}$ and $\sub{h}{\gm}$ can be defined by induction on
this inductive type.

@@
